---
title: 'Exercise: Make this document'
author: "Jack Rodenburg"
date: "2023-11-14"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***
Let’s see if you can make a document that looks *exactly like this* using **R Markdown.** Try to copy this document verbatum. Set the output to “html_document”

***

## 1. Insert this plot from the `iris` dataset
Here, I want you to insert a plot of three species of iris from the `iris` dataset. I have suppressed the printing of the code here. Some clues:

* It’s easy to produce boxplots using the formula syntax inside the `plot()` function.
* Use the code chunk option that prevents the code from being printed
* Use the code chunk option that shrinks the plot by 50%
* The three shades I used are “gray100”, “gray75” and “gray50”.

```{r echo = FALSE, out.width='50%', out.height='50%', fig.align = 'center'}
#library(ggplot2)
boxplot(Sepal.Length~Species, data=iris, main="Sepal Length of Three Species of Iris")
```




## 2. Conduct and report the results of an analysis
We can conduct a linear regression between the speed of a car and the distance it takes for the car to stop. This data is available in a dataset called `cars` that is pre-installed in R

```{r}
head(cars)
```
Let's plot it

```{r}
plot(dist~speed, data=cars, pch=19)
```
We can conduct the linear regression with speed as the independent variable and distance as the dependent variable:
```{r}
fit.cars=lm(dist~speed, data=cars)
summary(fit.cars)
```
## 3. Create a table to present results


Table Header^2^ | Second Header
------------- | -------------
Table Cell | Cell 2
Cell 3 | Cell 4 




