---
title: "Excercise: Make this document"
author: "Ken Kugel"
date: "2023-11-14"
output: html_document
---
Let’s see if you can make a document that looks *exactly like this* using **R Markdown**. Try to copy this document verbatum. Set the output to “html_document”

# 1. Insert this plot from the iris dataset

- Here, I want you to insert a plot of three species of iris from the `iris` dataset. I have suppressed the printing of the code here. Some clues:
  - It’s easy to produce boxplots using the formula syntax inside the `plot()` function.
  - Use the code chunk option that prevents the code from being printed
  - Use the code chunk option that shrinks the plot by 50%
  - The three shades I used are “gray100”, “gray75” and “gray50”.

```{r plot, echo=FALSE}
#iris
boxplot(Sepal.Length~Species, data= iris, xlab= "Species", ylab= "Sepal_Length", col=c("grey100", "grey75", "grey50"))
title("Sepal Length of Three Species of Iris")
```

# 2. Conduct and report the results of an analysis
We can conduct a linear regression between the speed of a car and the distance it takes for the car to stop. This data is available in a dataset called cars that is pre-installed in R.

```{r}
head(cars)
```

Let's plot it:

```{r}
plot(dist~speed, data=cars, pch=19)

```

We can conduct the linear regression with speed as the independent variable and distance as the dependent variable:
```{r}
fit.cars=lm(dist~speed, data=cars)
summary(fit.cars)
```

# 3. Create a table to present results
Let's organize the results as a table:
```{r}

```





